Dominance Regions for Imaginary $\bfg$-vectors

### 2020-06-15 dominance_regions.tex
Transforming inequalities
Correct(?) transformation of inequalities
The proof of Lemma 3.7 stopped making sense so I am quitting, we need to check the inequalities in the statement

  \begin{lemma}
    For $i\ge2$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align*}
      u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
      u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
    \end{align*}

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[-] (0,0) -- (5,-2.113);
        \draw[-] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[below right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

    For $i=2j$, $j>0$, and $\lambda\in\cI$, we get $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]

>>>>

  \begin{lemma}
    \label{le:transformed inequalities}
    Let $A=(a_{ij})$ be an invertible $2\times 2$ matrix.
    Under the action of $A$, the region inside $\RR^2$ defined by the inequality $rx+sy\le t$ is transformed to the region defined by the inequality \[\frac{ra_{22}-sa_{21}}{a_{11}a_{22}-a_{12}a_{21}}x + \frac{-ra_{12}+sa_{11}}{a_{11}a_{22}-a_{12}a_{21}}y\le t.\]
  \end{lemma}
  \begin{proof}
    Assume $r,s,t\ne0$, the cases when one of these vanishes follows by the continuity of the transformation.
    Observe that the points $\big(\frac{t}{r},0\big)$ and $\big(0,\frac{t}{s}\big)$ lie on the boundary line of the region defined by the inequality $rx+sy\le t$.
    These are transformed under the action of $A$ into the points $\big(a_{11}\frac{t}{r},a_{21}\frac{t}{r}\big)$ and $\big(a_{12}\frac{t}{s},a_{22}\frac{t}{s}\big)$, respectively, which one readily checks lie along the purported boundary of the image region.
    By the linearity of this transformation of $\RR^2$, we see that either both the domain region and image region contain the origin or both do not, in particular this implies that the inequalities go in the same direction.
  \end{proof}

  \begin{lemma}
    For $i\ge2$ and $\lambda\in\cI$, the region $\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_{i,-}x+u_{i-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
      \label{ineq:2} u_{i+1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:3} -u_{i-1,-}x+u_{i,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \label{ineq:4} -u_{i-1,-}x-u_{i-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
    \end{align}

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[-] (0,0) -- (5,-2.113);
        \draw[-] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[below right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
        \node at (4.5,-4) {\eqref{ineq:1}};
        \node at (2.5,-0.5) {\eqref{ineq:2}};
        \node at (-3,1.75) {\eqref{ineq:3}};
        \node at (-5.5,-3) {\eqref{ineq:4}};
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

    For $i=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_{t_i}(\phi_{t_i}\lambda)\subset\RR^2$ is given by the inequalities 
    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
    We inductively compute the region $\phi_{t_{2j}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{t_{2j}}^{-1}=\phi_{t_2}^{-j}$.

    \subsubsection*{Claim:} For $k>0$, $\phi_{t_{2k}}^{-1}\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ is the region determined by the inequalities 
    \begin{align*}
      \tag{a} u_{2k,-}x+u_{2k-1,+}y &\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2;\\
      \tag{b} u_{2k+1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \tag{c} -u_{2k-1,-}x+u_{2k,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2;\\
      \tag{d} -u_{2k-1,-}x-u_{2k-2,+}y &\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2.
    \end{align*}

    We see from \eqref{eq:backward two step mutation}, that $\lambda\in\cI$ implies the boundary ray for $\cC_{t_{2j}}(\phi_{t_{2j}}\lambda)$ corresponding to ($\ddagger$) lies entirely in the region in which $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$ of determinant 1.
    By Lemma~\ref{le:transformed inequalities}, the inequality ($\ddagger$) transforms into the inequality $-cx-y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2$.
